### 2022-02-04 README.Rmd
add continuous integration

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/maualithicspaper/master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/maualithicspaper/master?urlpath=rstudio) [![.github/workflows/knit-in-docker.yml](https://github.com/benmarwick/maualithicspaper/actions/workflows/knit-in-docker.yml/badge.svg)](https://github.com/benmarwick/maualithicspaper/actions/workflows/knit-in-docker.yml)
